### 2015-02-10 fundamentals/intro.tex

The \Cyclus next-generation fuel cycle simulator is the result of design
choices made to:
\begin{itemize}
\item support access to the tool by fuel cycle analysts and other users,
\item encourage developer extensions,
\item enable plug-and-play comparison of modeling methodologies,
\item and address a range of analysis types, levels of detail, and analyst sophistication.
\end{itemize}
Historically, nuclear fuel cycle simulators have calculated
fuel cycle mass balances and performance metrics derived from them using software
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized
system dynamics modeling platforms. To date, current tools are either static, fleet-based,
privately distributed, or all of the above. Each of these qualities presents a
challenge to modeling fidelity, generality, efficiency, robustness, and
scientific transparency.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that
can be compared among fuel cycle options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions between fuel cycles, and many other
measures of performance can be expressed in terms of these metrics. For example,
economic feasibility is often measured in levelized cost of electricity (\gls{LCOE}), requiring calculation of
lifetime fuel costs and electricity generation,
while environmental performance might be measured by spent fuel volume,
  toxicity, or mined uranium.  A meta-analysis of fuel cycle systems studies identified over two dozen unique quantitative metrics spanning economics and cost, environmental stainability and waste management impacts, safety, security and nonproliferation, resource adequacy and utilization, among others. With few exceptions, these metrics are derived from mass balances calculated by a fuel cycle simulator. *** shameless plug for some of our work! :)  Citation: Flicker, M. E., Schneider, E. A. and P. Campbell, "Evaluation Criteria for Analyses of Nuclear Fuel Cycles," Trans. Am. Nucl. Soc. 111, November 2014 ***

However, methods for calculating those metrics vary among simulators. Some model the
system of facilities, economics, and materials in static equilibrium, while
other simulators capture the dynamics of the system.
Similarly, while some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators can *** deleted overspecialization here and below since it struck me as a judgment call rather than objective statement ***
model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have excellent
capability in economics while models affecting transformations in material isotopics or the effects of isotopics on technology performance are
neglected.   *** would be useful to give an example here of a simulator that suffers from overspecification ***

Historically, the national laboratories have driven development and regulated
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010},
\gls{DANESS}\cite{van_den_durpel_daness_2009},
\gls{DYMOND}\cite{yacout_modeling_2005}, and
\gls{NFCSim}\cite{schneider_nfcsim:_2005}.  Outside the national laboratories,
researchers have created new nuclear fuel cycle simulation tools when existing
tools were not available or not sufficiently general to calculate their metrics
of interest.  With limited access to the national
laboratory tools and a need to customize them for research purposes,
universities and private industry researchers have ``reinvented the wheel'' by
developing tools of their own from scratch and tailored to their own needs, for
example \gls{CAFCA}\cite{guerin_impact_2009} and
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}.
*** I would put COSI into the first category of lab tools, to which you could add ORION.  Nothing else springs to mind here, but I'm sure a quick lit review would reveal some university developed models that were used for a few specific tasks, then forgotten ***

\Cyclus emerged from a line of tools seeking to break this practice.
Its precursor,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, originated within \gls{INL} and sought
\gls{ORION}\cite{}, *** lost me here... sought ORION? Also the next sentence seems abrupt... which lessons learned? ***  and
to provide generic regional capability.  Based on lessons learned from
Version 1, the
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to
provide more generality and an extensible interface to facilitate
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2}
effort by implementing increased modularity and encapsulation.  The result is
a dynamic simulator that treats both materials and facilities discretely, with
an architecture that permits multiple and variable levels of
fidelity. The simulator's agent-based framework for tracking the
transformation and trade of resources between autonomous entities with customizable behavior and objectives is an innovation not pursued by any existing fuel cycle simulator.   *** changed 'greatly improves upon' because it's subjective, also removed mention of institutions, regions here as the meaning of those terms in Cyclus has not yet been defined ***

\subsection{Motivation}
% Gently reiterate the above need.
% There should be a hero narrative here
% There was a gap in the capabilities of simulators.
% \Cyclus, a hero, came in to fill that gap.
*** I'm inspired to crank up the Bonnie Tyler :)  'I need a hero!' ***

The \Cyclus paradigm enables targeted contribution and collaboration within the nuclear fuel cycle analysis community. This essential capability, absent in previous simulators where user customization and extensibility were not design objectives, comes about through the \emph{modular and open architecture} of \Cyclus.
Additionally, \Cyclus facilitates direct comparison of modeling methodologies with
\emph{agent interchangeability}.
Finally, \Cyclus is applicable to a broader range of
fidelities, scales, and applications than other simulators.
due to the flexibility and generality
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}

>>>>

The \Cyclus next-generation fuel cycle simulator is the result of design
choices made to:
\begin{itemize}
\item support access to the tool by fuel cycle analysts and other users,
\item encourage developer extensions,
\item enable plug-and-play comparison of modeling methodologies,
\item and address a range of analysis types, levels of detail, and analyst sophistication.
\end{itemize}

Historically, nuclear fuel cycle simulators have calculated
fuel cycle mass balances and performance metrics derived from them using software
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized
system dynamics modeling platforms. To date, current tools are either static, fleet-based,
privately distributed, or all of the above. Each of these qualities presents a
challenge to modeling fidelity, generality, efficiency, robustness, and
scientific transparency.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
levelized cost of electricity (\gls{LCOE}), requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental stainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while models affecting transformations in
material isotopics or the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} code is problem-oriented
in this way.

Historically, domestic national laboratories have driven development and regulated
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010},
\gls{DANESS}\cite{van_den_durpel_daness_2009},
\gls{DYMOND}\cite{yacout_modeling_2005}, and
\gls{NFCSim}\cite{schneider_nfcsim:_2005}.
Internationally, other laboratories have created their own as well, such as
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
and
\gls{ORION}\cite{worrall_scenario_2007}.
Outside the national laboratories,
researchers have created new nuclear fuel cycle simulation tools when existing
tools were not available or not sufficiently general to calculate their metrics
of interest.  With limited access to the national
laboratory tools and a need to customize them for research purposes,
universities and private industry researchers have ``reinvented the wheel'' by
developing tools of their own from scratch and tailored to their own needs, for
example \gls{CAFCA}\cite{guerin_impact_2009}.

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006},
originated within \gls{INL} and sought to provide generic regional capability.
Based on lessons learned from Version 1, the \acrshort{GENIUSv2} Version
2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to provide more
generality and an extensible interface to facilitate collaboration.  The
\Cyclus project then improved upon the \acrshort{GENIUSv2} effort by
implementing increased modularity and encapsulation.  The result is a dynamic
simulator that treats both materials and facilities discretely, with an
architecture that permits multiple and variable levels of fidelity. The
simulator's agent-based framework for tracking the transformation and trade of
resources between autonomous regional and institutional entities with
customizable behavior and objectives is an innovation not pursued by any
existing fuel cycle simulator.

\subsection{Motivation}
% Gently reiterate the above need.
% There should be a hero narrative here
% There was a gap in the capabilities of simulators.
% \Cyclus, a hero, came in to fill that gap.

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community. This essential capability, absent in
previous simulators where user customization and extensibility were not design
objectives, comes about through the \emph{modular and open architecture} of
\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators.  due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.
